Chapter 4

### 2021-08-07 thesis_chapter_4.Rmd
added initial vector maps

library(tidyverse)
library(flextable)
library(tidync)
library(ncdf4)
library(lubridate)
library(gridExtra)
library(ggpubr)

@@

>>>>

library(tidyverse)
library(flextable)
library(tidync)
library(ncdf4)
library(lubridate)
library(gridExtra)
library(ggpubr)
library(jpeg)
library(gridExtra)

@@

map_chp4A <- rasterGrob(as.raster(readJPEG("figures/chapter_4/chapter_4_vectormap_summer.jpeg")))
map_chp4B <- rasterGrob(as.raster(readJPEG("figures/chapter_4/chapter_4_vectormap_autumn.jpeg")))
map_chp4C <- rasterGrob(as.raster(readJPEG("figures/chapter_4/chapter_4_vectormap_winter.jpeg")))
map_chp4D <- rasterGrob(as.raster(readJPEG("figures/chapter_4/chapter_4_vectormap_spring.jpeg")))

ggarrange(map_chp4A, map_chp4B, map_chp4C, map_chp4D)
